Improving reproducibility of scientific software using Nix/NixOS: A case study on the preCICE ecosystem

### 2024-05-17 paper/paper.tex
Extend tutorials section with all pitfalls

The preCICE tutorials included in the distribution cannot only be used as reference examples on how to couple different solvers, but also to verify functionality of solver and adapter installations by executing them.
To this end, we execute all 23 tutorials of the distribution such that each participant option is at least run once. We do not compare results, but only test whether the cases complete.
We test inside the NixOS VM and also in an ad-hoc shell environment provided by the \texttt{nix develop} command. All tests pass except the \textit{Turek-Hron FSI3} and the \textit{flow over heated plate steady state} cases.
We could not build swak4foam, an add-on to OpenFOAM, which is needed in the Turek-Hron FSI3 tutorial.
The official preCICE VM uses a prebuilt version of swak4foam, but also patching the prebuilt binary did not work.
The dependency is, however, no longer required in the v202404.0 release of the distribution.
The flow over heated plate steady state tutorial requires Code\_Aster. Even though we manage to package the solver, we observe a segmentation fault at runtime when the python code tries to call a Fortran subroutine -- a problem we did not manage to debug.

>>>>

The preCICE tutorials included in the distribution cannot only be used as reference examples on how to couple different solvers, but also to verify functionality of solver and adapter installations by executing them.
To this end, we execute all 23 tutorials of the distribution such that each participant option is at least run once. We do not compare results, but only test whether the cases complete.
We test inside the NixOS VM and also in an ad-hoc shell environment provided by the \texttt{nix develop} command. All tests pass except the \textit{Turek-Hron FSI3}, parts of the \textit{partitioned heat conduction}, parts of the \textit{perpendicular flap}, and the \textit{flow over heated plate steady state} cases.
We could not build swak4foam, an add-on to OpenFOAM, which is needed in the Turek-Hron FSI3 tutorial and the OpenFOAM participants of the partitioned heat conduction tutorial.
The official preCICE VM uses a prebuilt version of swak4foam, but also patching the prebuilt binary did not work.
The dependency is, however, no longer required in the v202404.0 release of the distribution.
We could, moreover, not package the third-party solids4foam solver, which is one of many options in the perpendicular flap tutorial. 
The flow over heated plate steady state tutorial requires Code\_Aster. Even though we manage to package the solver, we observe a segmentation fault at runtime when the python code tries to call a Fortran subroutine -- a problem we did not manage to debug.
